Supplmentary material - A plot is worth a thousand tests: assessing residual diagnostics with visual inference

### 2023-03-14 paper_comparison/appendix.Rmd
update subject allocation equation

\begin{equation*}
D =
C - \sum_{i}I(f_i\text{ exists in }L_{s}) - \sum_{i}\sum_{j\neq i}I(f_if_j\text{ exists in }L_{s}) - \sum_{i}\sum_{j\neq i}\sum_{k\neq j}I(f_if_jf_k\text{ exists in }L_{s})
\end{equation*}

\normalsize
where $C$ is a sufficient large constant such that $D > 0$. If $L_{s}$ is empty, we define $D = 0$.

The distance is measuring how different a lineup is from the set of lineups allocated to the subject in terms of factor values. Thus, the algorithm is trying to allocate the most different lineup to a subject.

>>>>

\begin{equation*}
D =
C - \sum_{1\leq i \leq q}I(f_i\text{ exists in }L_{s}) - \sum_{\substack{1\leq i \leq q-1 \\ i < j \leq q}}I(f_if_j\text{ exists in }L_{s}) - \sum_{\substack{1\leq i \leq q - 2 \\ i < j \leq q - 1 \\ j < k \leq q}}I(f_if_jf_k\text{ exists in }L_{s})
\end{equation*}

\normalsize
where $C$ is a sufficiently large constant such that $D > 0$. If $L_{s}$ is empty, we define $D = 0$.

The distance is measuring how different a lineup is from the set of lineups allocated to the subject in terms of factor values. Thus, the algorithm will try to allocate the most different lineup to a subject.
